---
title: "Project-One-Group-3"
author: "Jasmine Dogu, Christos Chen, Brian Wimmer - Group 3"
date: "01/11/2021"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: paper
  pdf_document:
    toc: yes
---


#Cleaning the Data 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, cache = TRUE)
#Import packages 
library(tidyverse)
library(tidytext)
library(textdata)
#install.packages("tidyselect")
library(tidyselect)
library(stringr)
library(caret)
library(e1071)
library(rpart)
library(RTextTools)
library(tm)
library(DMwR)
library(DT)
#install.packages("topicmodels")
library(tm)
library(plotly)
#install.packages("LDAvis")
library(LDAvis)
library(qdap)
library(topicmodels)
library(ggplot2)
library(googleLanguageR)
library(cld2)
library(wordnet)
library(qdapDictionaries)
library(datasets)
library(dplyr)
#install.packages("reticulate")
library(reticulate)
set.seed(03092000)
```

#About the Dataset
We will be using the “Spam Text Message Classification” dataset from Kaggle. It can be found [here](https://www.kaggle.com/team-ai/spam-text-message-classification).

The data consists of 5157 observations. Each observation is labeled “spam” or “ham”, with a base rate of 13% for spam. For reference, “ham” is a normal and non-spam text message. Each observation includes the message containing text.

#Background Research
We also wanted to do some background research regarding spam text messages to get an idea of how big a problem it is. We were extremely surprised to find that it was even more prominent than we expected. We discovered that around 3% of all text messages are spam related and that nearly 43 million Americans lost $10.5 billion to cellular text/call spams (in 2018). We also found information regarding steps that wireless providers utilize to minimize spam messages, including machine learning and artificial intelligence.


```{r}
#reading in the dataset 
df <- read.csv("/cloud/project/Datasets/Text_Message_Classification.csv")
head(df)
str(df)
head(df,5)
```

```{r}
library(wordnet)
library(textstem)
library(qdapDictionaries)
library(qdap)
library(iconv)

#CorpusList <-  iconv(, to ="utf-8")

dfCorpus = Corpus(VectorSource(df))  
#dfCorpus = as.character(dfCorpus)
inspect(dfCorpus) 

clean_corpus <- function(corpus) {
  # Remove punctuation
  corpus <- tm_map(corpus, removePunctuation(), lazy=TRUE)
  # Transform to lower case
  corpus <- tm_map(corpus, tolower(corpus, as.character()), lazy=TRUE)
  # Remove stopwords and strip whitespace
  corpus <- tm_map(corpus, removeWords(), words = stopwords("en"), stripWhitespace(), lazy=TRUE)
  # Lemmatize
  corpus <- tm_map(corpus, lemmatize_strings(corpus, as.vector()), lazy=TRUE)
  return(corpus)
}


?removePunctuation
?stripWhitespace
?lemmatize_strings
?tm_map
?content_transformer  #convert everything to the correct data type within the corpus

clean_corpus(dfCorpus)

```


```{r}
#Datasets for later 
df_spam <- filter(df, df$Category =="spam")
df_ham <-filter(df, df$Category =="ham")


#Removing punctuation
df2 = df %>% 
  select(Message) 

tm_map(df2, lemmatize_strings)

#%>%
# replace_contraction() 

df2$Message <- (str_replace_all(df2$Message, "[[:punct:]]", " "))


head(df2)

df_xx = df2 %>%
  unnest_tokens(word, "Message")  %>%




head(df_xx)

df_xx <- df_xx %>% 
  anti_join(stop_words)


  
df_xx <- filter(df_xx, !str_detect(word, "na")) #filtering out the na's in messages
df_xx
```

corpus[[1]]
[1] " earnest roughshod document serves workable primer regions recent history make 
terrific th-grade learning tool samuel beckett applied iranian voting process bard 
black comedy willie loved another trumpet blast may new mexican cinema -bornin "
> corpus <- tm_map(corpus, lemmatize_strings)
> corpus[[1]]
[1] "earnest roughshod document serve workable primer region recent history make 
terrific th - grade learn tool samuel beckett apply iranian vote process bard black 
comedy willie love another trumpet blast may new mexican cinema - bornin"

# SPAM Filtering
```{r}
#Removing punctuation
df2_spam = df_spam %>% 
  select(Message) 
#%>%
  #lemmatize_words(df$Message)

head(df2_spam)

df2_spam$Message <- (str_replace_all(df2_spam$Message, "[[:punct:]]", " "))
head(df2_spam)

df_xx_spam = df2_spam %>%
  unnest_tokens(word, "Message")
head(df_xx_spam)

df_xx_spam <- df_xx_spam %>% 
  anti_join(stop_words)

#%>%
 # replace_contraction()
  
df_xx_spam <- filter(df_xx_spam, !str_detect(word, "na")) #filtering out the na's in messages
df_xx_spam
```


# HAM Filtering 
```{r}
#Removing punctuation
df2_ham = df_ham %>% 
  select(Message) 
#%>%
  #lemmatize_words(df$Message)

head(df2_ham)

df2_ham$Message <- (str_replace_all(df2_ham$Message, "[[:punct:]]", " "))
head(df2_ham)

df_xx_ham = df2_ham %>%
  unnest_tokens(word, "Message")
head(df_xx_ham)

df_xx_ham <- df_xx_ham %>% 
  anti_join(stop_words)

#%>%
 # replace_contraction()
  
df_xx_ham <- filter(df_xx_ham, !str_detect(word, "na")) #filtering out the na's in messages
df_xx_ham
```





# Joined Count
```{r}
head(df_xx %>%
  count(df_xx$word, sort = TRUE), 20)
df_xx_count <- df_xx %>%
  count(word, sort=TRUE)
head(df_xx,5)
```

#Joined Sentiment 
```{r}
library(textdata)
get_sentiments('afinn') #generic table (word vs value)

df_sentiment_affin <- 
  df_xx %>%
  inner_join(get_sentiments("afinn")) # pull out only sentiment words

#View(df_sentiment_affin)
```

#SPAM Sentiment
```{r}
library(textdata)
get_sentiments('afinn') #generic table (word vs value)

df_sentiment_affin_spam <- 
  df_xx_spam %>%
  inner_join(get_sentiments("afinn")) # pull out only sentiment words

View(df_sentiment_affin_spam)
```

#HAM Sentiment
```{r}
library(textdata)
get_sentiments('afinn') #generic table (word vs value)

df_sentiment_affin_ham <- 
  df_xx_ham %>%
  inner_join(get_sentiments("afinn")) # pull out only sentiment words

View(df_sentiment_affin_ham)
```



#Joined Sentiment Chart
```{r}
table(df_sentiment_affin$value)


ggplot(data = df_sentiment_affin, 
       aes(x=value)
        )+
  geom_histogram()+
  ggtitle("Spam/Ham Classification Sentiment Range")+
  theme_minimal()


```


#SPAM Sentiment Chart
```{r}
table(df_sentiment_affin_spam$value)


ggplot(data = df_sentiment_affin_spam, 
       aes(x=value)
        )+
  geom_histogram()+
  ggtitle("Spam Text Sentiment Range")+
  theme_minimal()

```

#HAM Sentiment Chart
```{r}
table(df_sentiment_affin_ham$value)


ggplot(data = df_sentiment_affin_ham, 
       aes(x=value)
        )+
  geom_histogram()+
  ggtitle("Ham Text Sentiment Range")+
  theme_minimal()
```


# Base Rate Analysis
```{r}
print(table(df$Category))
```

```{r}
print(prop.table(table(df$Category)))
```
At 13.41%, this is clearly a skewed data set, aka rare event.

# Base Rate Pie Chart
```{r, message = FALSE, warnings = FALSE}
#creating pie chart for base rate
count.data <- data.frame(
  class = c("Ham", "Spam"),
  n = c(4825, 747),
  prop = c(86.59, 13.41)
)
mycols <- c("#474d84","#8d84ac")

# Add label position
count.data <- count.data %>%
  arrange(desc(class)) %>%
  mutate(lab.ypos = cumsum(prop) - 0.5*prop)
count.data
br<- ggplot(count.data, aes(x = 2, y = prop, fill = class)) +
  geom_bar(stat = "identity", color = "white") +
  coord_polar(theta = "y", start = 0)+
  geom_text(aes(y = lab.ypos, label = prop), color = "white")+
  scale_fill_manual(values = mycols) +
  theme_void()+
  xlim(0.5, 2.5)
br
#ggsave(br,file="base_rate.png", bg = "transparent")
```

# Data Cleaning 

```{r}
#remove stop words, perform stemming/maybe lemmatization, handle aprosthropes, handle contractions, deal with numbers (?), spell correction if needed, language, SMOTE, account for text

head(df)

#View(stop_words)

df <- df %>% 
      mutate(Message = tolower(Message)) %>%
     for (row in dataFrame) {
       for (x in row ){
         if(x == stop_words)
         str_remove(df, x, "")
       }
     }

df <- df %>% anti_join(stop_words) #tidytext package
      

```


```{r}

df_xx_count$word <- as.factor(df_xx_count$word) 
str(df_xx_count)

tokenword_plot = ggplotly(ggplot(
  data = head(df_xx_count, 30),
  aes(x = fct_reorder(word,n),
      y = n)
  ) + 
  geom_col() + 
  coord_flip()+
  theme_light()+
  xlab("Token Words")+
    ylab("Count")
  )
tokenword_plot

df_xx <- tibble(df_xx)
```

#Creating Unigrams and Bigrams 
```{r}
#Bigrams 
df_xx_ngrams_2 <- df2 %>%
  unnest_tokens(word, Message, token = "ngrams", n=2)

head(datatable(df_xx_ngrams_2), 20)

#Trigrams
df_xx_ngrams_3 <- df2 %>%
  unnest_tokens(word, Message, token = "ngrams", n=3)

head(datatable(df_xx_ngrams_3), 20)
```


```{r}
id <- rownames(df)
df_tf <- cbind(id=id, df)
df_tf
#------ Here, df = data_math_tf in Prof Wright's code 


#Placing everything in one column and adding "other id" back in


#Removing punctuation and NAs
df_tf$Message <- (str_replace_all(df_tf$Message, "[[:punct:]]", " "))

df_tf$Message <- (str_remove_all(df_tf$Message, "NA")) 
df_tf

#Counting of words, with ID

word_count_id <- df_tf %>%
  unnest_tokens(word, Message) %>%
  count(id, word, sort = TRUE)

head(word_count_id, 8)

total_words_id <- word_count_id %>% 
  group_by(id) %>% 
  summarize(total = sum(n))

head(total_words_id, 12)

journal_words_id <- left_join(word_count_id, total_words_id)

journal_words_id <- journal_words_id %>%
  bind_tf_idf(word, id, n)

datatable(journal_words_id)

```


# Topic Modeling - Latent Dirichlet Allocation
```{r}
install.packages('topicmodels')
library(topicmodels)

data("AssociatedPress")
AssociatedPress
```

```{r}
#function handles unbalanced classification problems using the SMOTE method
#synthetic Minority Over Sampling Technique
#library(smotefamily)

#dat_plot = SMOTE(dat[,1:2],  # feature values
#              as.numeric(dat[,3]),  # class labels
#              K = 3, dup_size = 0)  # function parameters
```

```{r}
#Regular Expressions
df_regEx <- df
df_regEx['Free'] <- NA
df_regEx['Currency_Symbol'] <- NA
df_regEx['Digits'] <- NA
df_regEx['Link'] <- NA
df_regEx['Call'] <- NA
df_regEx['Mobile_Phone'] <- NA
df_regEx['XXX'] <- NA
df_regEx['Symbol'] <- NA
df_regEx['Please'] <- NA
df_regEx['Reply_Yes'] <- NA
df_regEx['FreeMsg'] <- NA
df_regEx['Won_Win'] <- NA
df_regEx['Eighteen'] <- NA

head(df_regEx)
```


```{r}
library(tidyverse)

df_regEx$Currency_Symbol <- sapply(df_regEx$Message,str_detect, pattern = "\\$|£")
df_regEx$Free <- sapply(df_regEx$Message,str_detect, pattern = "([Ff][Rr][Ee][Ee])|([Uu][Rr][Gg][Ee][Nn][Tt])")
df_regEx$Digits <- sapply(df_regEx$Message,str_detect, pattern = "\\d{4,10}")
df_regEx$Link <- sapply(df_regEx$Message,str_detect, pattern = "([Ww]{3})|([Hh][Tt][Tt][Pp][Ss])|([Cc][Oo][Mm])")
df_regEx$Call <- sapply(df_regEx$Message,str_detect, pattern = "[Cc][Aa][Ll][Ll]")
df_regEx$Mobile_Phone <- sapply(df_regEx$Message,str_detect, pattern = "([Mm][Oo][Bb][Ii][Ll][Ee])|([Pp][Hh][Oo][Nn][Ee])")
df_regEx$XXX <- sapply(df_regEx$Message,str_detect, pattern = "[Xx]{3}")
df_regEx$Symbol <- sapply(df_regEx$Message,str_detect, pattern = "\\?|\\!")
df_regEx$Please <- sapply(df_regEx$Message,str_detect, pattern = "[Pp][Ll][Ee][Aa][Ss][Ee]")
df_regEx$Reply_Yes <- sapply(df_regEx$Message,str_detect, pattern = "([Yy][Ee][Ss])|([Nn][Oo])|([Rr][Ee][Pp][Ll][Yy]\\s[Yy][Ee][Ss])|([Rr][Ee][Pp][Ll][Yy])")
df_regEx$FreeMsg <- sapply(df_regEx$Message,str_detect, pattern = "[Ff][Rr][Ee][Ee][Mm][Ss][Gg]")
df_regEx$Won_Win <- sapply(df_regEx$Message,str_detect, pattern = "[Ww][OoIi][Nn]")
df_regEx$Eighteen <- sapply(df_regEx$Message,str_detect, pattern = "18+?")
regEx_removed <- df_regEx %>%
  select(-c("Category","Message"))
regEx_removed<- ifelse(regEx_removed==FALSE,0,1)
df_regEx<- cbind(df_regEx$Category, regEx_removed)
colnames(df_regEx)[1] <- "Category"
df_regEx<- as.data.frame(df_regEx)
df_regEx$Category <- ifelse(df_regEx$Category=='ham',0,1)  #if ham, 0, if spam 1
unique(df_regEx$Category)
str(df_regEx)
View(df_regEx)
```

#SMOTE using SVM
```{r}
#Creating a copy of the data
smote = SMOTE( kind='svm' )
X_smote, Y_smote = smote.fit_transform( X_data, Y_data )
```






