---
title: "Project-One-Group-3"
author: "Jasmine Dogu, Christos Chen, Brian Wimmer - Group 3"
date: "01/11/2021"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: paper
  pdf_document:
    toc: yes
---



```{r}
#Import packages 

library(tidyverse)
library(tidytext)
library(textdata)
install.packages("tidyselect")
library(tidyselect)
library(stringr)
library(DT)
install.packages("topicmodels")
library(tm)
library(plotly)
install.packages("LDAvis")
library(LDAvis)
library(topicmodels)

```



#Cleaning the Data 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, cache = TRUE)
library(ggplot2)
library(dplyr)
set.seed(03092000)
```

#About the Dataset
We will be using the “Spam Text Message Classification” dataset from Kaggle. It can be found [here](https://www.kaggle.com/team-ai/spam-text-message-classification).

The data consists of 5157 observations. Each observation is labeled “spam” or “ham”, with a base rate of 13% for spam. For reference, “ham” is a normal and non-spam text message. Each observation includes the message containing text.

#Background Research
We also wanted to do some background research regarding spam text messages to get an idea of how big a problem it is. We were extremely surprised to find that it was even more prominent than we expected. We discovered that around 3% of all text messages are spam related and that nearly 43 million Americans lost $10.5 billion to cellular text/call spams (in 2018). We also found information regarding steps that wireless providers utilize to minimize spam messages, including machine learning and artificial intelligence.


```{r}
#reading in the dataset 
df <- read.csv("/cloud/project/Datasets/Text_Message_Classification.csv")
head(df,5)
```

```{r}
#Removing punctuation

df2 = df %>% 
  select(Message)

df2$Message <- (str_replace_all(df2$Message, "[[:punct:]]", " "))
head(df2)

df_xx = df2 %>%
  unnest_tokens(word, "Message")
head(df_xx)

df_xx <- df_xx %>% 
  anti_join(stop_words)

df_xx <- filter(df_xx, !str_detect(word, "na"))

```

```{r}

head(df_xx %>%
  count(df_xx$word, sort = TRUE), 20)

df_xx_count <- df_xx %>%
  count(word, sort=TRUE)

df$Category <- ifelse(df$Category=='ham',0,1)
head(df,5)
```

```{r}
print(table(df$Category))
```

```{r}
print(prop.table(table(df$Category)))
```
At 13.41%, this is clearly a skewed data set, aka rare event.

```{r, message = FALSE, warnings = FALSE}
count.data <- data.frame(
  class = c("Ham", "Spam"),
  n = c(4825, 747),
  prop = c(86.59, 13.41)
)
mycols <- c("#474d84","#8d84ac")
# Add label position
count.data <- count.data %>%
  arrange(desc(class)) %>%
  mutate(lab.ypos = cumsum(prop) - 0.5*prop)
count.data
br<- ggplot(count.data, aes(x = 2, y = prop, fill = class)) +
  geom_bar(stat = "identity", color = "white") +
  coord_polar(theta = "y", start = 0)+
  geom_text(aes(y = lab.ypos, label = prop), color = "white")+
  scale_fill_manual(values = mycols) +
  theme_void()+
  xlim(0.5, 2.5)
br
#ggsave(br,file="base_rate.png", bg = "transparent")
```


```{r}

df_xx_count$word <- as.factor(df_xx_count$word) 
str(df_xx_count)

tokenword_plot = ggplotly(ggplot(
  data = head(df_xx_count, 30),
  aes(x = fct_reorder(word,n),
      y = n)
  ) + 
  geom_col() + 
  coord_flip()+
  theme_light()+
  xlab("Token Words")+
    ylab("Count")
  )
tokenword_plot

df_xx <- tibble(df_xx)
```

#Creating Unigrams and Bigrams 
```{r}
#Bigrams 
df_xx_ngrams_2 <- df2 %>%
  unnest_tokens(word, Message, token = "ngrams", n=2)

head(datatable(df_xx_ngrams_2), 20)

#Trigrams
df_xx_ngrams_3 <- df2 %>%
  unnest_tokens(word, Message, token = "ngrams", n=3)

head(datatable(df_xx_ngrams_3), 20)
```


```{r}
id <- rownames(df)
df_tf <- cbind(id=id, df)
df_tf
#------ Here, df = data_math_tf in Prof Wright's code 


#Placing everything in one column and adding "other id" back in


#Removing punctuation and NAs
df_tf$Message <- (str_replace_all(df_tf$Message, "[[:punct:]]", " "))

df_tf$Message <- (str_remove_all(df_tf$Message, "NA")) 
df_tf

#Counting of words, with ID

word_count_id <- df_tf %>%
  unnest_tokens(word, Message) %>%
  count(id, word, sort = TRUE)

head(word_count_id, 8)

total_words_id <- word_count_id %>% 
  group_by(id) %>% 
  summarize(total = sum(n))

head(total_words_id, 12)

journal_words_id <- left_join(word_count_id, total_words_id)

journal_words_id <- journal_words_id %>%
  bind_tf_idf(word, id, n)

datatable(journal_words_id)

```





# Exploratory Data Analysis


# Sentiment Analysis 


# Topic Modeling - Latent Dirichlet Allocation
```{r}
install.packages('topicmodels')
library(topicmodels)

data("AssociatedPress")
AssociatedPress


```

```{r}
#function handles unbalanced classification problems using the SMOTE method
#synthetic Minority Over Sampling Technique
#library(smotefamily)

#dat_plot = SMOTE(dat[,1:2],  # feature values
#              as.numeric(dat[,3]),  # class labels
#              K = 3, dup_size = 0)  # function parameters
```


